---
title: "Challenge Notes"
output: html_document
---

#Challenge 1

```{r echo=TRUE}
v<- c("Stately,","plump","Buck","Mulligan","came","from","the","stairhead,","bearing","a","bowl","of","lather","on","which","a","mirror","and","a","razor","lay","crossed")
v[seq(from=1, to=22, by=3)] 

```

This is what I did for the challenge, below is the code that was shown in class. 

```{r echo=TRUE}
#Example code from girl in class, how the module does it
Ulysses <- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed")

e<- gsub("[[:punct:]]","",Ulysses) 
#So the punctuation won't count as a command

xspt<- c(unlist(strsplit(Ulysses, " ")))
#I'm not quite sure why you have to unlist it

xspt[seq(from=1, to=22, by=3)] 

```



#Challenge 2
```{r}
m<-matrix(data=1:80, nrow=8, ncol=10, byrow=FALSE)
x<-m[ ,c(2,3,6)] #Leave row empty, use C() to do multiple columns
x<-m[c(6,8), ] #Leave column empty, use c() to do multiple rows
x<-m[c(2:6), c(2:9)]
```
Okay I know this is right because I can see it on my RStudio console but to be honest I don't know why I'm not getting any output on my HTML file. I tried typing echo=TRUE, eval=TRUE, and cache=TRUE in the r code chunks and neither one worked.

 
#Challenge 3
```{r echo=TRUE}
a<- array (data=400:1, dim= c(5,5,4,4))

a[1,1,1,2]
# =300
a[2,3,2, ]
# =364 264 164 64
a[1:5, 1:5,3,3]
# =the section of the matrix that is 3,3; 150:126
```

For the Primates list, I know that I want the name to be primates. Then maybe a separate list for each bullet point? 
#Challenge 4
```{r}
c1<- 'Cercopithecidae'
h1<- 'Hylobatidae'
h2<- 'Hominidae'
Catarrhini<-list(c1, h1, h2)
names(Catarrhini) <- "Catarrhini"
c3<- 'Cebidae'
a1<- 'Atelidae'
p1<- 'Pitheciidae'
Platyrrhini<- list(c3, a1, p1)
names(Platyrrhini) <- "Platyrrhini"
Anthropoidea<- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- c("Anthropoidea", "Anthropoidea")
Tarsioidea <- list("Tarsiidae")
names(Tarsioidea) <- "Tarsioidea"
Haplorhini<- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- c("Haplorhini","Haplorhini")
c4<- 'Cheirogaleidae'
l1<- 'Lepilemuridae'
i1<- 'Indriidae'
l2<- 'Lemuridae'
d1<- 'Daubentoniidae'
Lemuroidea<- list(c4,l1,i1,l2,d1)
names(Lemuroidea) <- c("Lemuroidea", "Lemuroidea","Lemuroidea","Lemuroidea","Lemuroidea")
l4<- 'Lorisidae'
g1<- 'Galagidae'
Lorisoidea<- list(l4,g1)
names(Lorisoidea) <- c("Lorisoidea", "Lorisoidea")
Strepsirhini<- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- c("Strepsirhini","Strepsirhini")
Primates<- list(Haplorhini,Strepsirhini)
names(Primates) <- c("Primates","Primates")
```
Again, I'm not really sure why there is no output on my HTML file.

#Challenge 5
```{r echo=TRUE}
q<- matrix(data=c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2), nrow=5, ncol=3, byrow=TRUE)
df<- as.data.frame(q)
df[ ,2] <- as.logical(df[ ,2])
df[ ,3] <- as.factor(df[ ,3])
 str(df)
```

Side-note: I was messed up before because I was trying to do str(q), which is what I named the matrix, but I renamed it df after I set it up as a data frame
